Bootstrap Confidence Intervals for Regression Discontinuity Designs with Uniform Kernels

### 2016-02-21 main_paper.tex
Fix minor error in notation for algorithms
I forgot a few subscripts and powers in defining the ATE estimates.
This commit adds them.
Add more macros for formatted variable names
I don't like typing all of the varieties of 'B', so I'm converting
some of them to macros for now.

\cite{calonico2014} resolve the problem by deriving the analytical form of the first-order bias and correcting it directly. To obtain correct coverage the confidence interval needs not only to be re-centered to correct the bias, but also rescaled to allow for the additional variability introduced by the bias correction. Their approach relies on obtaining a bias-corrected  estimator, $\hat{\tau}^{bc}$ and its adjusted variance. It is important first to note that the first-order bias term itself will depend on the bandwidth $h_{n}$. The approximate bias term can be described as:
\begin{align*}
     \E[\hat{\tau}(h_{n})|\chi_{n}]-\tau=& h_{n}^{2}\mathsf{B}(h_{n})\{1+o_{p}(1)\}\\
     \mathsf{B}(h_{n})=&\frac{\mu_{+}^{(2)}}{2!}\mathfrak{B}_{+}(h_{n})-\frac{\mu_{-}^{(2)}}{2!}\mathfrak{B}_{-}(h_{n})
   \end{align*}
where $\mathfrak{B}_{+}(h_{n})$ and $\mathfrak{B}_{-}(h_{n})$ are observed quantities that depend on the data, kernel and $h_{n}$. The plug-in bias-corrected estimator then requires estimates for the second derivatives of the conditional mean from above and below the cutoff, $\mu_{+}^{(2)}$ and $\mu_{-}^{(2)}$. CCT propose using a conventional local quadratic estimator, i.e. one order higher than the polynomial used to obtain $\hat{\tau}$,  using a (potentially) different pilot bandwidth $b_{n}$.
\begin{align*}
     \hat{\tau}^{bc}(h_{n}, b_{n})=& \hat{\tau}-h_{n}^{2}\hat{\mathsf{B}}(h_{n},b_{n})\\
     \hat{\mathsf{B}}(h_{n})=&\frac{\hat{\mu}_{+}^{(2)}(b_{n})}{2!}\mathfrak{B}_{+}(h_{n})-\frac{\hat{\mu}_{-}^{(2)}(b_{n})}{2!}\mathfrak{B}_{-}(h_{n})
   \end{align*}
By incorporating the contribution of both $\hat{\tau}(h_{n})$ and $\hat{\mathsf{B}}(h_{n},b_{n})$ to the asymptotic distribution of the estimator, CCT obtain a robust confidence interval with a different asymptotic variance in general. So under Assumptions \ref{A1} and \ref{A2}, if $n\min\{h_{n}^{5}, b_{n}^{5}\}max\{h_{n}^{2}, b_{n}^{2}\}\rightarrow 0$ and $n\min\{h_{n}, b_{n}\}\rightarrow \infty$ and $\kappa \max\{h_{n},b_{n}\}< \kappa_{0}$, they show that
\begin{align}
  T^{rbc}(h_{n}, b_{n})=\frac{\hat{\tau}^{bc}(h_{n}, b_{n})-\tau}{\sqrt{V^{bc}(h_{n}, b_{n})}}\rightarrow_{d}N(0,1), \text{        }V^{bc}(h_{n}, b_{n})=V(h_{n})+C^{bc}(h_{n}, b_{n})\\
 \end{align}
where the additional term $C^{bc}(h_{n}, b_{n})$ depends on the (asymptotic) variability of the bias estimate used for correction as well as its correlation with the original RD estimator $\hat{\tau}(h_{n})$.\footnote{The details of the formulas are currently ommitted from this paper since their form is not relevant to the bootstrap procedure innovation proposed. The details can be found at CCT Appendix.}  Under these conditions we can construct a valid confidence interval for $\tau$ given by
 \begin{align}
  I^{rbc}(h_{n}, b_{n})=\left[\left(\hat{\tau}(h_{n})-h_{n}^{2}\hat{\mathsf{B}}(h_{n},b_{n})\right)\pm \Phi^{-1}_{1-\frac{\alpha}{2}}\sqrt{V(h_{n})+C^{bc}(h_{n}, b_{n})} \right]
 \end{align}

@@

Essentially, we apply CCT's insight that a polynomial one order higher can capture the first-order bias behavior and create a bootstrap procedure that can correctly mimic the behavior of the bias present in the original estimator. For such, for a chosen bandwidth, we estimate a local quadratic regression the same way CCT suggested but then create bootstrap data by imposing the local quadratic functional form as the DGP. Then, in the ``bootstrap data'' the DGP is known. Let the ``true'' treatment effect under the bootstrap DGP be denoted by $\tau^{*}$. We then estimate the treatment effect using the (misspecified) local linear estimator, $\hat{\tau}^{*}$ to the generated data. Hence, the bias for a specific bootstrap data is given by $\tau^{*}-\hat{\tau}^{*}$. More importantly, by generating new bootstrapped data based on the same quadratic DGP and its residual's distribution, we can obtain an estimate of the first-order bias (the part that is captured by $\hat{\mathsf{B}}(h_{n},b_{n})$ in CCT's formulas on Section \ref{background}) in the original estimate by averaging across the bias in all $B$ bootstrapped data estimates,i.e., $\tau^{*} - \sum_{i = 1}^{B} \hat{\tau}_{ i}^{*}$. Algorithm~\ref{Alg1} describes this procedure step-by-step for clarity.

\begin{algorithm}[Bias estimation]\label{Alg1}
  Assume $h_n$ and $b_n$ are bandwidths as described by Assumption~\ref{A3} and
  define
  \begin{align}
    I^-(h) &= \{i : h < X_i < 0\}, &
    I^+(h) &= \{i : 0 < X_i < h\}.
  \end{align}
  Also define $M^-(h_n)$ and $M^+(h_n)$ to be the number of elements in
  $I^-(h_n)$ and $I^+(h_n)$ respectively.
  \begin{enumerate}
  \item Estimate the local polynomials $g_{p+1}^+$ and $g_{p+1}^-$ as defined by
    Equation --- and define the residuals
    \begin{equation}
      \label{eq:1}
      \hat\varepsilon_i =
      \begin{cases}
        Y_i - \hat g_{p+1}^-(X_i) & \textif\ X_i < 0 \\
        Y_i - \hat g_{p+1}^+(X_i) & \otherwise
      \end{cases}
    \end{equation}
  \item Repeat the following steps $B_1$ times to produce a sequence of bootstrap
    estimates $\hat\tau_1^*,\dots,\hat\tau_{B_1}^*$. For the $k$th step:
    \begin{enumerate}
    \item Draw an i.i.d. sample of size $M^-(b_n)$ from
      $\{\hat\varepsilon_i : i \in I^-(b_n)\}$ and one of size $M^+(b_n)$ from
      $\{\hat\varepsilon_i : i \in I^+(h_n)\}$. Let $\varepsilon_i^{*-}$ and
      $\varepsilon_i^{*+}$ denote the $i$th element of each sample and construct
      \begin{align}
        \label{eq:2}
        Y_i^{*-} &= \hat g_{p+1}^-(X_i^{*-}) + \varepsilon_i^{*-} &
        Y_i^{*+} &= \hat g_{p+1}^+(X_i^{*+}) + \varepsilon_i^{*+}
      \end{align}
    \item Calculate $\hat\mu_+^*$ and $\hat\mu_-^*$ as
      \begin{align}
        \hat\mu_-^*
        &= \argmin_{\beta_0} \min_{\beta_1,\dots,\beta_p}
          \sum_{i = 1}^{M^-(h_n)} (Y_i^{*-} -
          (\beta_0 + \beta_1 X_i^{*-} + \cdots + \beta X_i^{*-}))^2 \\
        \hat\mu_+^*
        &= \argmin_{\beta_0} \min_{\beta_1,\dots,\beta_p}
          \sum_{i = 1}^{M^+(h_n)} (Y_i^{*+} -
          (\beta_0 + \beta_1 X_i^{*+} + \cdots + \beta X_i^{*+}))^2
      \end{align}
    \item Save $\hat\mu_+^* - \hat\mu_-^*$ as $\hat\tau^*_k$.
    \end{enumerate}
  \item Calculate the bias estimator as
    \begin{equation}
      \label{eq:4}
      \hat\Delta = \tfrac{1}{B_1} \sum_{k=1}^{B_1} \hat\tau^*_k -
      \big[\hat g_{p+1}^+(0) - \hat g_{p+1}^-(0)\big].
    \end{equation}
  \end{enumerate}
\end{algorithm}

@@

\begin{algorithm}[Confidence intervals]\label{Alg2}
  Define $I^-$, $I^+$, $M^-$, and $M^+$ as in Algorithm~\ref{Alg1}.
  \begin{enumerate}
  \item Estimate the local polynomials $g_{p+1}^+$ and $g_{p+1}^-$ as defined by
    Equation --- and define the residuals
    \begin{equation}
      \label{eq:6}
      \hat\varepsilon_i =
      \begin{cases}
        Y_i - \hat g_{p+1}^-(X_i) & \textif\ X_i < 0 \\
        Y_i - \hat g_{p+1}^+(X_i) & \otherwise
      \end{cases}
    \end{equation}
  \item Repeat the following steps $B_2$ times to produce a sequence of bootstrap
    estimates $\hat\tau_1^{\prime*},\dots,\hat\tau_B^{\prime*}$. For the $k$th step:
    \begin{enumerate}
    \item Draw an i.i.d. sample of size $M^-(b_n)$ from
      $\{\hat\varepsilon_i : i \in I^-(b_n)\}$ and one of size $M^+(b_n)$ from
      $\{\hat\varepsilon_i : i \in I^+(h_n)\}$. Let $\varepsilon_i^{*-}$ and
      $\varepsilon_i^{*+}$ denote the $i$th element of each sample and construct
      \begin{align}
        \label{eq:2}
        Y_i^{*-} &= \hat g_{p+1}^-(X_i^{*-}) + \varepsilon_i^{*-} &
        Y_i^{*+} &= \hat g_{p+1}^+(X_i^{*+}) + \varepsilon_i^{*+}
      \end{align}
    \item Calculate $\hat\mu_+^*$ and $\hat\mu_-^*$ as
      \begin{align}
        \hat\mu_-^*
        &= \argmin_{\beta_0} \min_{\beta_1,\dots,\beta_p}
          \sum_{i = 1}^{M^-(h_n)} (Y_i^{*-} -
          (\beta_0 + \beta_1 X_i^{*-} + \cdots + \beta X_i^{*-}))^2 \\
        \hat\mu_+^*
        &= \argmin_{\beta_0} \min_{\beta_1,\dots,\beta_p}
          \sum_{i = 1}^{M^+(h_n)} (Y_i^{*+} -
          (\beta_0 + \beta_1 X_i^{*+} + \cdots + \beta X_i^{*+}))^2
      \end{align}
    \item Apply Algorithm~\ref{Alg1} to the bootstrapped data set,
      \begin{equation*}
        (Y_1^{*-}, X_1^{*-}),\dots,(Y_{M^-(b_n)}^{*-},X_{M^-(b_n)}^{*-}),
        (Y_1^{*+}, X_1^{*+}),\dots,(Y_{M^+(b_n)}^{*+},X_{M^+(b_n)}^{*+}),
      \end{equation*}
      using the same bandwidths $h_n$ and $b_n$ that are used in the rest of
      this algorithm but reestimating all of the local polynomials on the
      bootstrap data. Let $\hat\Delta^*$ represent the bias estimate returned
      by Algorithm~\ref{Alg1}.
    \item Save the bias-corrected estimate
      $\hat\mu_+^* - \hat\mu_i^* - \hat\Delta^*$ as $\hat\tau_k^{\prime*}$.
    \end{enumerate}
  \item Define the confidence interval endpoints $\hat\ell(\alpha)$ and
    $\hat u(\alpha)$ as the $\alpha/2$ and $1-\alpha/2$ quantiles of the
    empirical CDF of $\hat\tau_1^{\prime*},\dots,\hat\tau_{B_2}^{\prime*}$.
  \end{enumerate}
\end{algorithm}

>>>>

\cite{calonico2014} resolve the problem by deriving the analytical form of the first-order bias and correcting it directly. To obtain correct coverage the confidence interval needs not only to be re-centered to correct the bias, but also rescaled to allow for the additional variability introduced by the bias correction. Their approach relies on obtaining a bias-corrected  estimator, $\hat{\tau}^{bc}$ and its adjusted variance. It is important first to note that the first-order bias term itself will depend on the bandwidth $h_{n}$. The approximate bias term can be described as:
\begin{align*}
     \E[\hat{\tau}(h_{n})|\chi_{n}]-\tau=& h_{n}^{2}\Bs(h_{n})\{1+o_{p}(1)\}\\
     \Bs(h_{n})=&\frac{\mu_{+}^{(2)}}{2!}\Bf_{+}(h_{n})-\frac{\mu_{-}^{(2)}}{2!}\Bf_{-}(h_{n})
   \end{align*}
where $\Bf_{+}(h_{n})$ and $\Bf_{-}(h_{n})$ are observed quantities that depend on the data, kernel and $h_{n}$. The plug-in bias-corrected estimator then requires estimates for the second derivatives of the conditional mean from above and below the cutoff, $\mu_{+}^{(2)}$ and $\mu_{-}^{(2)}$. CCT propose using a conventional local quadratic estimator, i.e. one order higher than the polynomial used to obtain $\hat{\tau}$,  using a (potentially) different pilot bandwidth $b_{n}$.
\begin{align*}
     \hat{\tau}^{bc}(h_{n}, b_{n})=& \hat{\tau}-h_{n}^{2}\hat{\Bs}(h_{n},b_{n})\\
     \hat{\Bs}(h_{n})=&\frac{\hat{\mu}_{+}^{(2)}(b_{n})}{2!}\Bf_{+}(h_{n})-\frac{\hat{\mu}_{-}^{(2)}(b_{n})}{2!}\Bf_{-}(h_{n})
   \end{align*}
By incorporating the contribution of both $\hat{\tau}(h_{n})$ and $\hat{\Bs}(h_{n},b_{n})$ to the asymptotic distribution of the estimator, CCT obtain a robust confidence interval with a different asymptotic variance in general. So under Assumptions \ref{A1} and \ref{A2}, if $n\min\{h_{n}^{5}, b_{n}^{5}\}max\{h_{n}^{2}, b_{n}^{2}\}\rightarrow 0$ and $n\min\{h_{n}, b_{n}\}\rightarrow \infty$ and $\kappa \max\{h_{n},b_{n}\}< \kappa_{0}$, they show that
\begin{align}
  T^{rbc}(h_{n}, b_{n})=\frac{\hat{\tau}^{bc}(h_{n}, b_{n})-\tau}{\sqrt{V^{bc}(h_{n}, b_{n})}}\rightarrow_{d}N(0,1), \text{        }V^{bc}(h_{n}, b_{n})=V(h_{n})+C^{bc}(h_{n}, b_{n})\\
 \end{align}
where the additional term $C^{bc}(h_{n}, b_{n})$ depends on the (asymptotic) variability of the bias estimate used for correction as well as its correlation with the original RD estimator $\hat{\tau}(h_{n})$.\footnote{The details of the formulas are currently ommitted from this paper since their form is not relevant to the bootstrap procedure innovation proposed. The details can be found at CCT Appendix.}  Under these conditions we can construct a valid confidence interval for $\tau$ given by
 \begin{align}
  I^{rbc}(h_{n}, b_{n})=\left[\left(\hat{\tau}(h_{n})-h_{n}^{2}\hat{\Bs}(h_{n},b_{n})\right)\pm \Phi^{-1}_{1-\frac{\alpha}{2}}\sqrt{V(h_{n})+C^{bc}(h_{n}, b_{n})} \right]
 \end{align}

@@

Essentially, we apply CCT's insight that a polynomial one order higher can capture the first-order bias behavior and create a bootstrap procedure that can correctly mimic the behavior of the bias present in the original estimator. For such, for a chosen bandwidth, we estimate a local quadratic regression the same way CCT suggested but then create bootstrap data by imposing the local quadratic functional form as the DGP. Then, in the ``bootstrap data'' the DGP is known. Let the ``true'' treatment effect under the bootstrap DGP be denoted by $\tau^{*}$. We then estimate the treatment effect using the (misspecified) local linear estimator, $\hat{\tau}^{*}$ to the generated data. Hence, the bias for a specific bootstrap data is given by $\tau^{*}-\hat{\tau}^{*}$. More importantly, by generating new bootstrapped data based on the same quadratic DGP and its residual's distribution, we can obtain an estimate of the first-order bias (the part that is captured by $\hat{\Bs}(h_{n},b_{n})$ in CCT's formulas on Section \ref{background}) in the original estimate by averaging across the bias in all $B$ bootstrapped data estimates,i.e., $\tau^{*} - \sum_{i = 1}^{B} \hat{\tau}_{ i}^{*}$. Algorithm~\ref{Alg1} describes this procedure step-by-step for clarity.

\begin{algorithm}[Bias estimation]\label{Alg1}
  Assume $h_n$ and $b_n$ are bandwidths as described by Assumption~\ref{A3} and
  define
  \begin{align}
    I^-(h) &= \{i : h < X_i < 0\}, &
    I^+(h) &= \{i : 0 < X_i < h\}.
  \end{align}
  Also define $M^-(h_n)$ and $M^+(h_n)$ to be the number of elements in
  $I^-(h_n)$ and $I^+(h_n)$ respectively.
  \begin{enumerate}
  \item Estimate the local polynomials $g_{p+1}^+$ and $g_{p+1}^-$ as defined by
    Equation --- and define the residuals
    \begin{equation}
      \label{eq:1}
      \hat\varepsilon_i =
      \begin{cases}
        Y_i - \hat g_{p+1}^-(X_i) & \textif\ X_i < 0 \\
        Y_i - \hat g_{p+1}^+(X_i) & \otherwise
      \end{cases}
    \end{equation}
  \item Repeat the following steps $B_1$ times to produce a sequence of bootstrap
    estimates $\hat\tau_1^*,\dots,\hat\tau_{B_1}^*$. For the $k$th step:
    \begin{enumerate}
    \item Draw an i.i.d. sample of size $M^-(b_n)$ from
      $\{\hat\varepsilon_i : i \in I^-(b_n)\}$ and one of size $M^+(b_n)$ from
      $\{\hat\varepsilon_i : i \in I^+(h_n)\}$. Let $\varepsilon_i^{*-}$ and
      $\varepsilon_i^{*+}$ denote the $i$th element of each sample and construct
      \begin{align}
        \label{eq:2}
        Y_i^{*-} &= \hat g_{p+1}^-(X_i^{*-}) + \varepsilon_i^{*-} &
        Y_i^{*+} &= \hat g_{p+1}^+(X_i^{*+}) + \varepsilon_i^{*+}
      \end{align}
    \item Calculate $\hat\mu_+^*$ and $\hat\mu_-^*$ as
      \begin{align}
        \hat\mu_-^*
        &= \argmin_{\beta_0} \min_{\beta_1,\dots,\beta_p}
          \sum_{i = 1}^{M^-(h_n)} (Y_i^{*-} -
          (\beta_0 + \beta_1 X_i^{*-} + \cdots + \beta_p (X_i^{*-})^p))^2 \\
        \hat\mu_+^*
        &= \argmin_{\beta_0} \min_{\beta_1,\dots,\beta_p}
          \sum_{i = 1}^{M^+(h_n)} (Y_i^{*+} -
          (\beta_0 + \beta_1 X_i^{*+} + \cdots + \beta_p (X_i^{*+})^p))^2
      \end{align}
    \item Save $\hat\mu_+^* - \hat\mu_-^*$ as $\hat\tau^*_k$.
    \end{enumerate}
  \item Calculate the bias estimator as
    \begin{equation}
      \label{eq:4}
      \hat\Delta = \tfrac{1}{B_1} \sum_{k=1}^{B_1} \hat\tau^*_k -
      \big[\hat g_{p+1}^+(0) - \hat g_{p+1}^-(0)\big].
    \end{equation}
  \end{enumerate}
\end{algorithm}

@@

\begin{algorithm}[Confidence intervals]\label{Alg2}
  Define $I^-$, $I^+$, $M^-$, and $M^+$ as in Algorithm~\ref{Alg1}.
  \begin{enumerate}
  \item Estimate the local polynomials $g_{p+1}^+$ and $g_{p+1}^-$ as defined by
    Equation --- and define the residuals
    \begin{equation}
      \label{eq:6}
      \hat\varepsilon_i =
      \begin{cases}
        Y_i - \hat g_{p+1}^-(X_i) & \textif\ X_i < 0 \\
        Y_i - \hat g_{p+1}^+(X_i) & \otherwise
      \end{cases}
    \end{equation}
  \item Repeat the following steps $B_2$ times to produce a sequence of bootstrap
    estimates $\hat\tau_1^{\prime*},\dots,\hat\tau_B^{\prime*}$. For the $k$th step:
    \begin{enumerate}
    \item Draw an i.i.d. sample of size $M^-(b_n)$ from
      $\{\hat\varepsilon_i : i \in I^-(b_n)\}$ and one of size $M^+(b_n)$ from
      $\{\hat\varepsilon_i : i \in I^+(h_n)\}$. Let $\varepsilon_i^{*-}$ and
      $\varepsilon_i^{*+}$ denote the $i$th element of each sample and construct
      \begin{align}
        \label{eq:2}
        Y_i^{*-} &= \hat g_{p+1}^-(X_i^{*-}) + \varepsilon_i^{*-} &
        Y_i^{*+} &= \hat g_{p+1}^+(X_i^{*+}) + \varepsilon_i^{*+}
      \end{align}
    \item Calculate $\hat\mu_+^*$ and $\hat\mu_-^*$ as
      \begin{align}
        \hat\mu_-^*
        &= \argmin_{\beta_0} \min_{\beta_1,\dots,\beta_p}
          \sum_{i = 1}^{M^-(h_n)} (Y_i^{*-} -
          (\beta_0 + \beta_1 X_i^{*-} + \cdots + \beta_p (X_i^{*-})^p))^2 \\
        \hat\mu_+^*
        &= \argmin_{\beta_0} \min_{\beta_1,\dots,\beta_p}
          \sum_{i = 1}^{M^+(h_n)} (Y_i^{*+} -
          (\beta_0 + \beta_1 X_i^{*+} + \cdots + \beta_p (X_i^{*+})^p))^2
      \end{align}
    \item Apply Algorithm~\ref{Alg1} to the bootstrapped data set,
      \begin{equation*}
        (Y_1^{*-}, X_1^{*-}),\dots,(Y_{M^-(b_n)}^{*-},X_{M^-(b_n)}^{*-}),
        (Y_1^{*+}, X_1^{*+}),\dots,(Y_{M^+(b_n)}^{*+},X_{M^+(b_n)}^{*+}),
      \end{equation*}
      using the same bandwidths $h_n$ and $b_n$ that are used in the rest of
      this algorithm but reestimating all of the local polynomials on the
      bootstrap data. Let $\hat\Delta^*$ represent the bias estimate returned
      by Algorithm~\ref{Alg1}.
    \item Save the bias-corrected estimate
      $\hat\mu_+^* - \hat\mu_i^* - \hat\Delta^*$ as $\hat\tau_k^{\prime*}$.
    \end{enumerate}
  \item Define the confidence interval endpoints $\hat\ell(\alpha)$ and
    $\hat u(\alpha)$ as the $\alpha/2$ and $1-\alpha/2$ quantiles of the
    empirical CDF of $\hat\tau_1^{\prime*},\dots,\hat\tau_{B_2}^{\prime*}$.
  \end{enumerate}
\end{algorithm}
